\documentclass{extension}

%\usepackage{titling}
%\setlength{\droptitle}{10mm}

\usepackage[superscript]{cite}
\usepackage{hyperref}
\makeatletter
\renewcommand\@citess[1]{\textsuperscript{[#1]}}
\renewcommand\refname{Materials}

\newcommand{\mm}{\,$\mathrm{mm}$}
\newcommand{\m}{\,$\mathrm{m}$}
\newcommand{\uunit}{\,$\mathrm{W\,m^{-2}\,K}$}

\begin{document}

\title{Building Regulations Application \\[2mm]
Response to schedule of additional \\ information/details for 23/01851/FP}
\author{J. Mullaney}
\date{\today}

\maketitle

\vspace{5mm}

\section{Structure}
\begin{enumerate}
\item {\it Foundations to be to the approval of the District Building Surveyor}\\
I confirm that foundatations for the Porch and Extension will be inspected and approved by the District Building Surveyor prior to the commencement of any further construction. A note to this effect as been added to page 6 of the plans. No new foundations are needed for the Utility Room and WC (i.e., rear room).
\item {\it New walls should be suitably bonded to existing walls. i.e., using a proprietary wall starter kit.}\\
I confirm that new walls will be bonded to the existing walls using a wall starter kit such as SabreFix Stainless Steel Wall Starter Kit, or similar.\cite{starterkit} This has been added to plans and has, where necessary, been added to the Supporting Documentation.
\item {\it Wall plates should be strapped to new masonry walls every 2m, using galvanised steel straps at least 1m length.}\\
The only reference to wall plates in the original submission was on the plans for the porch. It has since been realised that they are not required, and so have been removed from the plans.
\item {\it Can you confirm the roof span? The proposed 120$\times$47 C16 joists appear slightly under spanned according to the Trada tables, at 2.4\,m maximum clear span.}\\
Thank you for pointing out this oversight. The clear span of the extension (study) is 2.36\,m, while the clear span of the rear room is 2.83\,m. So while the extension is just within the maximum clear span, the rear room is not. The rear room joists have now been upgraded to 145$\times$47 C24, which have a maximum clear span of 3.1\,m. Since the clear span of the extension is close to the maximum clear span for 120$\times$47 C16, these have now been upgraded to C24. The 120$\times$47 C16 floor joists in the rear room have also now been upgraded to C24, and the plans have been changed to show them supported by sleeper walls with a separation of 1.6\,m between supports. Section 3.3.1 of the Supporting Documentation has been changed accordingly.
\item {\it The new flat roof should be strapped to masonry walls where joists run parallel, across min 3x timbers with noggins every 1800 centres using 1.2m galvanised steel straps.}\\
A 1.2\,m galvanised steel strap has been added to the plans of the roof of the rear room and the study. In the case of the study it is tied to an existing masonry wall, while in the case of the rear room it is tied to the new rear wall. In both cases the straps extend over three joists. A plan of the substructure of study roof (showing joists, noggins and strap) has been added to the plans, and the Supporting Documentation has been changed accordingly.
\end{enumerate}

\section{Fire safety}
\begin{enumerate}
\item {\it The garage floor level should be a minimum 100\mm\ below the floor level to the new utility room.}\\
The utility floor is approx. 293\mm\ above the garage floor. This is now shown on the plans and described in Section 3.3.1 of the Supporting Documentation.
\item {\it The fire door to the garage from the utility room requires smoke seals and a self-closing device.}\\
These have now been added to Section 3.3 of the Supporting Documentation and a note to this effect has been added to the plans.
\item {\it The flat roof covering should achieve BROOF(t4) rating.}\\According to the BBA certification (included as an additional document to this resubmission) 18\mm\ plywood with a fully-adhered 1.2\mm\ ClassicBond Non-reinforced EPDM membrane achieved ${\rm B_{ROOF}(t4)}$ standard when tested to tested to DD CEN/TS 1187:2012, Test 4 and classified to BS EN 13501-5:2005. To ensure this is achieved, the 18\mm\ OSB under the EPDM has been replaced with 18\mm\ plywood, as shown on the amended plans.
\end{enumerate}

\section{Resistance to moisture and contaminants}
\begin{enumerate}
\item {\it DPC should be 150mm above ground level linked with DPM/radon barrier, and tray DPC provided over the cavity}\\
All DPCs are a minimum of 150\mm\ above the ground level. This dimension is now shown on the plans where applicable. In the case of the study and porch, the DPC of the inner leaf is lapped with the DPM in the solid floor, as shown on the plans. Tray DPCs with stop ends have been added over the window and door openings in the rear wall to the rear room, with two weep holes, separated by no more than 450\mm , added per opening. Cavity trays and explanatory notes have been added to the plans, and the Supporting Documentation has been changed accordingly.
\item {\it Can you clarify the cavity wall insulation? Ie. K106 partial fill cavity board requires minimum 50\mm\ clear cavity.}\\
All insulation board in the masonry cavity walls -- front wall of study, \& back wall of rear-room -- has been changed to partial-fill (i.e., Kingspan K108 or similar; K106 is full-fill), with a 50\mm\ clear cavity. The U-value calculations have been altered accordingly. All insulation boards in stud walls -- porch, side wall of rear room, wall between rear room and garage -- have been changed to framing boards (i.e., Kingspan K112 or similar). A 25\mm\ clear cavity between the brick and stud walls has been added to the side wall. To maintain the wall thickness, the thickness of the insulation has been reduced to 100\mm , increasing the overall U-value of the wall to 0.33\,\uunit . Please note, however, that the heated towel rail has now been removed from the w/c, meaning no part of the rear room will be heated so thermal loss through the side wall will be minimal. Both the plans and the Supporting Documentation have been changed accordingly.
\item {\it A vapour barrier should be fitted to the warm side of the flat roof insulation. A breathable membrane is not required (Cutaway A and B)}\\
This has been amended on the plans.
\item {\it Can you confirm any existing ventilation to the front of the property, and how this will be maintained?}\\
The only existing ventilation to the front of the property (aside from current windows and doors) are two air bricks: one underneath the downstairs bay window, and another to the left of the front door. Both are now shown on the existing and proposed front elevations. Neither air bricks will be compromised by the proposed alterations.
\end{enumerate}

\section{Ventilation}
\begin{enumerate}
\item {\it Note: Background ventilation is required to all new windows/doors, at a rate of 8000mm2 for habitable rooms and kitchens, and 4000mm2 for bathrooms.}\\
Trickle vents will be included in all new window and door frames. A note to this effect has been added to the plans and Supporting Documentation.
\item {\it Can you confirm how purge ventilation is to be achieved to the study? Ie. opening window or extract mechanical ventilation.}\\
The window will include an opening mechanism to allow purge ventilation. A note to this effect has been added to the plans and Supporting Documentation.
\end{enumerate}

\section{Drainage}
\begin{enumerate}
\item {\it The new above ground drainage should be constructed in accordance with AD H1. Section 1.}\\
The routing of the soil pipe from the new downstairs WC has been significantly altered to reduce the length of the routing to the stack. The new soilpipe connects to a private sewer that runs along the boundary of the property of concern and the neighbouring property. Permission from the neighbour to excavate the private sewer has been sought and granted. The private sewer connects to a combined-use public sewer that runs along the back of the property. A connection to the private sewer is preferred as it will enable easier inspection from the nearby manhole (via camera or rods down the stack). The stack will be fitted with an AAV which is rated for external use.\cite{aav} The AAV will terminate above the highest waste entry point which will be the sink overflow (waste from the sink will flow into the soil pipe). Both the WC and sink will be fitted with traps. All pipework will be rigid uPVC. Below-ground pipework will sit on a 100\mm -thick bed of 5-10\mm\ gravel and be covered to at least 150\mm. The area surrounding the point where the soil pipe enters the ground will be finished with a concrete slab; in this region the pipe will be protected by a compressible material. A new page (8 of 8) has been added to the plans to show the layout of the proposed pipework, and the Supporting Documentation has ben changed accordingly.
\end{enumerate}

\section{Protection from falling, collision and impact}
\begin{enumerate}
\item {\it Any glazing within critical locations eg. less then 800mm between floor and sill level should be safety glazing in accordance with BS EN 12600}\\
A note has been added to the plans and Supporting Documentation stating that the study window must be installed with safety glazing.
\end{enumerate}

\section{Conservation of fuel and power}
\begin{enumerate}
\item {\it New doors and windows should achieve 1.4 U-value.}\\
A note has been added to the plans and Supporting Documentation stating that all new windows and doors should achieve a U-value of 1.4~\uunit .
\item {\it A 25mm strip of insulation should be provided at the edge of the floor slab to help prevent cold bridging.}\\
A 25\mm\ strip of insutation has been added to the plans as required.
\end{enumerate}

\section{Additional changes}
\begin{enumerate}
\item The construction of the solid floor in the study has been altered slightly. The 120\mm\ insulation layer now lies above an 85\mm -thick layer of concrete and directly below a 65\mm -thick cement screed. Previously the insulation lay below both the screed and the concrete. The new structure still complies with the insulation manufacturer's installation guidelines.
\end{enumerate}


\begin{thebibliography}{9}
\bibitem{starterkit} \href{https://www.screwfix.com/p/sabrefix-wall-starter-kit-stainless-steel/56037?kpid=56037&cm_mmc=Google-_-Datafeed-_-Building%20and%20Doors?kpid=KINASEKPID&cm_mmc=Google-_-TOKEN1-_-TOKEN2&gclid=EAIaIQobChMIvrnvoZmQgQMVjIFQBh3P7gMrEAQYAiABEgIWrvD_BwE&gclsrc=aw.ds}{Sabrefix Wall Starter Kit Stainless Steel}.
\bibitem{aav}\href{https://www.screwfix.com/p/floplast-push-fit-air-admittance-valve-black-110mm/35001} {FloPlast Push-Fit Air Admittance Valve Black 110mm}



\end{thebibliography}
\end{document}
